### 2018-12-14 Vortrag/slides/sections/ddplus.tex
Made end of slides nicer.

\begin{frame}{The \ddp\ algorithm}
	Zellers \textbf{extended} $dd$ algorithm \ddp\ deals with the following cases:
	\begin{enumerate}
		\item ``found (in $c_i$)'' \only<2->{$\Rightarrow$ continue search in $c_i$}
		\item ``interference'' \only<3->{$\Rightarrow$ search in $c_i$ while leaving $\bar{c_i}$ applied and vice versa}
		\item ``preference'' \only<4->{$\Rightarrow$ search in $c_i$ while leaving $\bar{c_i}$ applied}
		\item ``try again'' \only<5->{$\Rightarrow$ repeat search on same change set with twice as many subsets}
		%\item ``nothing left		
	\end{enumerate}
\end{frame}

@@

	\begin{columns}
		\begin{column}{0.475\textwidth}
			\begin{align*}
	     &\text{double \textbf{mult}(double z[], int n)}\\
	     &\{\\
	     	&\quad \text{int } i,j; \\
	     	&\quad i = 0; \\
	     	&\quad for(j = 0; j < n; j++)\{ \\
	     	&\quad 	\quad i = i + j + 1; \\
	     &	\quad 	\quad z[i] = z[i] * (z[0] + 1.0); \\
	     &	\quad \} \\
	     &	\quad \text{return } z[n]; \\
	    & \}
	\end{align*} 
		\end{column}
		\begin{column}{0.475\textwidth}

>>>>

\begin{frame}{The \ddp\ algorithm}
	Zeller's \textbf{extended} $dd$ algorithm \ddp\ deals with the following cases:
	\begin{enumerate}
		\item ``found (in $c_i$)'' \only<2->{$\Rightarrow$ continue search in $c_i$}
		\item ``interference'' \only<3->{$\Rightarrow$ search in $c_i$ while leaving $\bar{c_i}$ applied and vice versa}
		\item ``preference'' \only<4->{$\Rightarrow$ search in $c_i$ while leaving $\bar{c_i}$ applied}
		\item ``try again'' \only<5->{$\Rightarrow$ repeat search on same change set with twice as many subsets}
		%\item ``nothing left		
	\end{enumerate}
\end{frame}

@@

	\begin{columns}
		\begin{column}{0.475\textwidth}
			\texttt{
			\begin{align*}
	     &\text{double \textbf{mult}(double $z[]$, int $n$)}\\
	     &\{\\
	     	&\quad \text{int } i,j; \\
	     	&\quad i = 0; \\
	     	&\quad \text{for}(j = 0; j < n; j++)\{ \\
	     	&\quad 	\quad i = i + j + 1; \\
	     &	\quad 	\quad z[i] = z[i] * (z[0] + 1.0); \\
	     &	\quad \} \\
	     &	\quad \text{return } z[n]; \\
	    & \}
	\end{align*}
		} 
		\end{column}
		\begin{column}{0.475\textwidth}
